---
title: "CAD to USD exchange rate prediction"
author: "Fanli Zhou"
date: "2020/6/16"
output: 
  github_document:
    toc: true
    pandoc_args: --webtex
bibliography: report_refs.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(tidyverse)
```

```{r define functions and load data, echo=FALSE, message=FALSE}



```

# Summary

In this project, I attempted to predict CAD to USD exchange rates in 30 days given previous exchange rates. 



# Methods

## Data

The 



## Analysis Methods

ARIMA models, classic supervised learning models, and LSTM methods were used to predict CAD to USD exchange rates in 30 days given previous exchange rates. The Python programming language [@Python], the R programming language [@R] and the following Python/R packages were used: pandas [@mckinney-proc-scipy-2010], Numpy [@oliphant2006guide], Scipy [@mckinney-proc-scipy-2010], Scikit-learn [@pedregosa2011scikit], Matplotlib [@Hunter], Statsmodels [@seabold2010statsmodels], Keras [@chollet2015keras], Tensorflow [@abadi2016tensorflow], pmdarima [@pmdarima], tqdm [@da-Costa-Luis2019], LightGBM [@Ke2017LightGBMAH], requests [@chandra2015python], knitr [@knitr], tidyverse [@tidyverse], rjson [@rjson]. The code used to perform the analysis and create this report can be found here: https://github.com/flizhou/CAD_USD_exchange_rate_predictor.


# Results and Discussion




## Conclusions

In this analysis, I attempted to 

# Limitations
 
My analysis is 

# References